\documentclass{standalone}

\begin{document}

First of all anyone who wants to collaborate anything using this site need to verify themself. Then check for email verification to find actually this email is valid or not. Entering this site need to profile setup like registration. \\\\

\section*{3.1\hspace{0.3 cm} Resource Sharing}
\addcontentsline{toc}{section}{3.1\hspace{0.3 cm} Resource Sharing}

In this Project when anyone want to share resource like any type of departmental documents like conference paper, journal paper, thesis paper also can reference e-book or sharing any file that helps others. Also for higher studies who already has gone to the foreign country can also join this site and can share experiences.
\\\\

\section*{3.2\hspace{0.3 cm} Timeline for posting}

\addcontentsline{toc}{section}{3.2\hspace{0.3 cm} Timeline for posting} \vspace{0.3cm}

In this site there is timeline for anything posting in instantly. Anyone who already registered can post any educational related picture or blog, can share whats new with them. And also others also can see that if he/she logged in. This timeline is realtime means no need to refresh to see the new things, automatically updated anything. \\ \\

\section*{3.3\hspace{0.3 cm} The Faculty}
\addcontentsline{toc}{section}{3.3\hspace{0.3 cm} The Faculty} \vspace{0.3cm}

There are departments faculty members in the faculty section. Now These three departments software engineering, computer science and engineering and electrical and electronics engineering students can show their faculty members with information and contact with them .\\\\[1.4cm]

\section*{3.4\hspace{0.3 cm} The Online Market}
\addcontentsline{toc}{section}{3.4\hspace{0.3 cm} The Online Market} \vspace{0.3cm}


In varsity life, Students use different types of electrical things like mobile, laptop, monitor, desktop, playstation, keyboard, mouse, soundbox and different types of sports things. After one or two years things getting old as far they want to sell to others with half money or less as second hand things. Anyone can buy and sell these.\\[1.1cm]

\section*{3.5\hspace{0.3 cm} Department Curriculum}
\addcontentsline{toc}{section}{3.5\hspace{0.3 cm} Department Curriculum} \vspace{0.3cm}

There are also includes departments curriculum. Students can see their departments current semester course and upcoming semester courses and also see their subjective credit. These is the extra feature of these project for helping easily to students.\\\\

\end{document}